What's hot and what's not:\\Windowed developer topic analysis

### 2009-06-19 lda-paper.tex
more lda - paper changes    - [X] Add references?  • Some references are lacking; for example in “We mirrored the repositories and their revisions using software such as rsync, CVSSuck, softChange and bt2csv” (page 3) - [X]  Add more refernces "Others have demonstrated ..." -> some references would help - Count - [X] General case study metrics • Maybe some information regarding the number of analyzed commit per case studies could be useful to understand a little bit better the experiemnts.  - updated per each case study

Usually topic analysis is applied to the entire history of a project,
where as we suggest that more topics are probably local, if a
programmer is working on a story card, they might never deal with that
story card ever again. Thus that topic might be quite relevant to a
small window of time but never relevant ever again.  By applying topic
analysis locally to an iteration, both the developers and managers
might be able to see what were the topics of development during that
iteration, rather than the whole project.

@@

Grant et al.~\cite{scottcordy} have used an alternative technique,
called Independent Component Analysis to separate topic signals from
software code.

@@

We mirrored the repositories and their revisions using software such
as rsync, CVSSuck, \texttt{softChange} and bt2csv.
\texttt{softChange} provided a general schema for storing revisions
and grouped CVS revisions into commits. CVSSuck and rsync mirrored CVS
repositories while bt2csv mirrored web accessible BitKeeper
repositories.

@@

We have devised several techniques for visualizing these topics and
trends.  For all of these techniques if we find trends that have
continuous segments, then we plot those segments as joined
horizontally across time. One technique is the \emph{compact-trend-view},
shown in Figure \ref{fig:topicsmear} and Figure \ref{fig:zoomedsmear},
that displays trends as they occur on the time-based x-axis
(placement along the y-axis is arbitrary).  Another technique is
the \emph{trend-time-line}, shown in Figure \ref{fig:trendtimeline},
each trend gets it own distinct y-value, while the x-axis is time;
these topics are then each plotted on their own line across time as
they occur. Our final technique is the \emph{trend-histogram}, shown in Figure
\ref{fig:histogram} where we plot each trend on its own line but stack
up the segments of the trend, much like a histogram.

@@

We applied our tools and visualizations to the repositories of several
open source database systems: PostgreSQL, MaxDB and Firebird.

@@

When we examined PostgreSQL, we did not find many trends with two or
more topics, using a similarity of $7/10$. $7/10$ was chosen because
it preserved indepedant topics but seemed to be a borderline threshold
value where more serious trends started to appear.

@@

We tracked Firebird from August 2000 to January 2006. We found that with a
similarity of $7/10$ Firebird had far more continuous and
recurring trends than PostgreSQL.  The first large trend was segmented
across time but explicitly references one author \texttt{carlosga05}
and words like \emph{added}, \emph{fixed} and \emph{updated}.

@@

The plots we produced of MaxDB 7.500 were unlike those of the other
systems, as there was a period where no development occurred and
thus there were no topics or trends whatsoever (see the gap in Figure
\ref{fig:topicsmear}). Using a topic similarity of $7/10$ we evaluated
MaxDB 7.500. MaxDB 7.500's first period was from June 2004 to January
2005, and its second period was from June 2005 to June 2006.

>>>>

Usually topic analysis is applied to the entire history of a project~\cite{1321709,lukins2008,10.1109/ICPC.2007.13},
where as we suggest that more topics are probably local, if a
programmer is working on a story card, they might never deal with that
story card ever again. Thus that topic might be quite relevant to a
small window of time but never relevant ever again.  By applying topic
analysis locally to an iteration, both the developers and managers
might be able to see what were the topics of development during that
iteration, rather than the whole project.

@@

Grant et al.~\cite{scottcordy} and have used an alternative technique,
called Independent Component Analysis~\cite{delac} to separate topic signals from
software code.

@@

We mirrored the repositories and their revisions using software such
as rsync~\cite{rsync}, CVSsuck~\cite{cvssuck},
\texttt{softChange}~\cite{dmgseke2004}, and bt2csv~\cite{methodology}.
\texttt{softChange} provided a general schema for storing revisions
and grouped CVS revisions into commits. CVSsuck and rsync mirrored CVS
repositories while bt2csv mirrored web accessible BitKeeper
repositories.

@@

We have devised several techniques for visualizing these topics and
trends.  For all of these techniques if we find trends that have
continuous segments, then we plot those segments as joined
horizontally across time. One technique is the \emph{compact-trend-view},
shown in Figure \ref{fig:topicsmear} and Figure \ref{fig:zoomedsmear},
that displays trends as they occur on the time-based x-axis
(placement along the y-axis is arbitrary).  Another technique is
the \emph{trend-time-line}, shown in Figure \ref{fig:trendtimeline},
each trend gets it own distinct y-value, while the x-axis is time;
these topics are then each plotted on their own line across time as
they occur. Our final technique is the \emph{trend-histogram}, shown in Figure
\ref{fig:histogram} where we plot each trend on its own line but stack
up the segments of the trend, much like a histogram. Each topic has its top 10 words 
listed in descending order of frequency from top to bottom, this text is embedded inside the topic's box.
A trend has all of its topic text embedded side by side within the same trend box.

@@

We applied our tools and visualizations to the repositories of several
open source database systems: PostgreSQL, MaxDB and Firebird. The
total number of commits analyzed was over $66 000$.

@@

When we examined PostgreSQL's history from 1996 to 2004, which include
over $20 000$ commits. We did not find many trends with two or more
topics, using a similarity of $7/10$. $7/10$ was chosen because it
preserved indepedant topics but seemed to be a borderline threshold
value where more serious trends started to appear.

@@

We tracked Firebird from August 2000 to January 2006, we extracted comments from $38 000$ commits. We found that with a
similarity of $7/10$ Firebird had far more continuous and
recurring trends than PostgreSQL.  The first large trend was segmented
across time but explicitly references one author \texttt{carlosga05}
and words like \emph{added}, \emph{fixed} and \emph{updated}.

@@

The plots we produced of MaxDB 7.500 were unlike those of the other
systems, as there was a period where no development occurred and thus
there were no topics or trends whatsoever (see the gap in Figure
\ref{fig:topicsmear}). Using a topic similarity of $7/10$ we evaluated
MaxDB 7.500. MaxDB 7.500's first period was from June 2004 to January
2005, and its second period was from June 2005 to June 2006. There
were a total of $8 600$ commits analyzed.
